---
title: "Data Analysis Project"
author: "Nishant"
date: "11/08/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
#Abstract

#Problem
exploring the relations between the variable Education and other variables such as Fertility and Agriculture.

#Data
The data chosen here is the swiss dataset in R. 

Swiss Fertility and Socioeconomic Indicators (1888) Data

Standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888.

Format
A data frame with 47 observations on 6 variables, each of which is in percent, i.e., in [0, 100].

[,1]	Fertility	Ig, ‘common standardized fertility measure’
[,2]	Agriculture	% of males involved in agriculture as occupation
[,3]	Examination	% draftees receiving highest mark on army examination
[,4]	Education	% education beyond primary school for draftees.
[,5]	Catholic	% ‘catholic’ (as opposed to ‘protestant’).
[,6]	Infant.Mortality	live births who live less than 1 year.
All variables but ‘Fertility’ give proportions of the population.

Details
(paraphrasing Mosteller and Tukey):

Switzerland, in 1888, was entering a period known as the demographic transition; i.e., its fertility was beginning to fall from the high level typical of underdeveloped countries.

The data collected are for 47 French-speaking “provinces” at about 1888.

Here, all variables are scaled to [0, 100], where in the original, all but "Catholic" were scaled to [0, 1].




No omits where found.

##Scatter plot of the dataset.
```{r swiss, echo=FALSE}
pairs(swiss, panel = panel.smooth, main = "swiss data")
```
We will try to understand the relation between Education and fertility. There is major bunching in it.
```{r swiss}
plot(swiss$Fertility ~ swiss$Education)
summary(lm(Fertility ~ . , data = swiss))
```
Preliminary examination shows that a higher rate of Education Indicates lower amount of fertility
```{r swiss}
plot(swiss$Agriculture ~ swiss$Education)

```
This graph too indicates that agriculture is taken up by those with poorer education. Social and economic theories very well explain these observations.

#Model
We will use a linear regression model. We will use normal priors for Education.

#JAGS 
```{r swiss}
library("rjags")
mod1_string = " model {
    for (i in 1:length(y)) {
        y[i] ~ dbern(p[i])
        logit(p[i]) = int + b[1]*gravity[i] + b[2]*ph[i] + b[3]*osmo[i] + b[4]*cond[i] + b[5]*urea[i] + b[6]*calc[i]
    }
    int ~ dnorm(0.0, 1.0/25.0)
    for (j in 1:6) {
        b[j] ~ ddexp(0.0, sqrt(2.0)) # has variance 1.0
    }
} "
```




